SPARQL on the Open, Decentralised Web

### 2016-07-22 dissertation/introdefhistory.tex
don't break sentence

As noted in the previous section, objectivity may be challenged by a
researcher's intellectual investment in a certain field of study. I
admit that I have a very large intellectual investment in the success
of the Semantic Web. This section serves two purposes: It should give
the reader a good understanding of this intellectual investment, and
enable them to assess the impact of any subjective beliefs. Secondly,
it serves to clarify \emph{my} vision, which we noted in
Section~\ref{sec:nodef} is more important than to attempt a
definition. The vision strongly influences the motivation detailed in
Section~\ref{sec:motivation}.

>>>>

As noted in the previous section, objectivity may be challenged by a
researcher's intellectual investment in a certain field of study and I
admit that I have a very large intellectual investment in the success
of the Semantic Web. This section serves two purposes: It should give
the reader a good understanding of this intellectual investment, and
enable them to assess the impact of any subjective beliefs. Secondly,
it serves to clarify \emph{my} vision, which we noted in
Section~\ref{sec:nodef} is more important than to attempt a
definition. The vision strongly influences the motivation detailed in
Section~\ref{sec:motivation}.
